Research Notes

### 2018-03-06 writups/notes.tex

@@

Let's first consider the phase velocity. We traditionally think about the phase
velocity in 1D $v_{ph} = \frac{\omega(k)}{k}$, but in general it is the function
such that $\vec{k} \cdot \vec{r} - \omega t = \vec{k} \cdot \p*{\vec{r} -
\vec{v}_{ph}t}$ is constant (the phase of the wave). Thus, it must satisfy
$\vec{k} \cdot \vec{v}_{ph} = \omega$, and so one sensible choice is
$\vec{v}_{ph} = \frac{\omega \hat{k}}{\abs{\vec{k}}} = \frac{\omega
\vec{k}}{\abs{\vec{k}}^2}$. Thus, if we have some waveform $f(x, z, t)$, we can
estimate its phase velocity $\vec{v}_{ph}(x, z, t)$ by
\begin{equation}
    \vec{v}_{ph}(x, z, t) = \frac{\partial_t f
        \vec{\nabla}f}{\abs{\vec{\nabla}f}^2}.\label{eq:v_ph}
\end{equation}
This can be validated in the $f(x, z, t) \propto e^{i(\vec{k} \cdot \vec{x} -
\omega t)}$ case to give $\vec{v}_{ph} = \frac{\omega \vec{k}}{k^2}$. Note the
sign in \autoref{eq:v_ph}

>>>>

Let's first consider the phase velocity. We traditionally think about the phase
velocity in 1D $v_{ph} = \frac{\omega(k)}{k}$, but in general it is the function
such that $\vec{k} \cdot \vec{r} - \omega t = \vec{k} \cdot \p*{\vec{r} -
\vec{v}_{ph}t}$ is constant (the phase of the wave). Thus, it must satisfy
$\vec{k} \cdot \vec{v}_{ph} = \omega$, and so one sensible choice is
\begin{equation}
    \vec{v}_{ph} = \frac{\omega \hat{k}}{\abs{\vec{k}}}
        = \frac{\omega \vec{k}}{\abs{\vec{k}}^2}.
        \label{eq:v_ph}
\end{equation}

@@

Based on our phase velocity expression \autoref{eq:v_ph}, if we have some
waveform $f(x, z, t)$, we can estimate its phase velocity $\vec{v}_{ph}(x, z,
t)$ by
\begin{equation}
    \vec{v}_{ph}(x, z, t) = \frac{\partial_t f
        \vec{\nabla}f}{\abs{\vec{\nabla}f}^2}.\label{eq:v_ph}
\end{equation}
This can be validated in the $f(x, z, t) \propto e^{i(\vec{k} \cdot \vec{x} -
\omega t)}$ case to give $\vec{v}_{ph} = \frac{\omega \vec{k}}{k^2}$. Note the
sign in \autoref{eq:v_ph}
